---
title: "HW2"
author: "Joy Lin (jl84785)"
date: "2025-01-26"
output:
  html_document:
    df_print: paged
  pdf_document: default
---

## [GithubLink]()

# Question One

### Part A
```{r warning=FALSE, echo=FALSE}

library(ggplot2)
profs <- read.csv('profs.csv')
ggplot(profs,(aes(x=eval))) + geom_histogram(binwidth=.1, col='black', fill='blue') + labs(title='Distribution of Professor Evaluation')

```

The instructor’s average teaching evaluation score, on a scale of 1 to 5, for courses in the sample. The graph shows that the evaluation score on average is around the 3.5-4.5 range. There are some who are rated very low, being 2-3.


### Part B
```{r warning=FALSE, echo=FALSE}
ggplot(profs, (aes(x=eval))) + geom_boxplot(col='black', fill= "pink")+facet_wrap('native')+ labs(title = 'Distribution of Course Evaluation for Native and Non-Native Speakers')
```

The yes is referring to the professor that are native speaker while the no isn't. There seems to better evaluations for native speakers than non native speakers. This might be because students have a harder time understanding the professor explain the content, and give them a worse rating.

### Part C
```{r warning=FALSE, echo=FALSE}
ggplot(profs, (aes(x=eval))) + geom_histogram(binwidth = .1, col='black') + facet_wrap('gender') + labs(title='Distribution of Course Evaluation for Female and Male Professor')
```

The count is the amount of students that voted for that specific rating in the professor evaluation. Even though there seems to be more male ratings that female ones, there seems to be higher average ratings for males. This observation could indicate potential biases in the evaluations or differences in how students perceive and rate their professors based on gender. 


### Part D
```{r warning=FALSE, echo=FALSE}
ggplot(profs, (aes(x=beauty, y=eval)))+ geom_point()+ labs(title = "Beauty score vs Course Evaluation Score")
```

This plot illustrates the relationship between professors' beauty scores and their evaluation scores. Interestingly, the most attractive professors do not necessarily have the highest evaluation scores. It likely does not matter in how handsome or pretty a professor is.

# Question 2

### Plot 1
```{r warning=FALSE, echo=FALSE }
bikeshare=read.csv("bikeshare.csv")
suppressMessages(library(dplyr))

bikeshare1<-bikeshare %>% 
  group_by(hr) %>%
    summarize(mean(total))
colnames(bikeshare1)[2]<-"total"
ggplot(bikeshare1, (aes(x=hr, y=total)))+geom_line()+labs(title='Average Bike Rentals for Each Hour')

```


This line graph illustrates the average number of bike rentals by hour over the course of a day. The data reveal two significant peaks in rentals: one around 8:00 AM and another near 5:00 PM. These trends suggest that bike usage is notably higher in the morning as commuters head to work and in the evening as they return home. This pattern aligns with typical daily commuting behaviors, highlighting the bike's role as a convenient mode of transportation during peak commuting times.


### Plot 2
```{r warning=FALSE, echo=FALSE}
bikeshare2 <- suppressMessages(bikeshare %>%
  group_by(hr, workingday) %>%
  summarize(avg_total = mean(total, na.rm = TRUE)))
bikeshare2 <- bikeshare2 %>%
  mutate(workingday = ifelse(workingday == 1, "Working Day", "None Working Day"))
ggplot(bikeshare2, (aes(x=hr, y=avg_total)))+geom_line()+facet_grid('workingday')+labs(title='Average Bike Rentals for Each Hour')

```

This line graph displays the average number of bike rentals throughout a typical day, revealing two notable peaks: one around 8:00 AM and another near 5:00 PM. These peaks indicate a significant increase in bike usage during morning and evening hours. This pattern reflects common commuting habit emphasizing the bike's utility as a convenient transportation option during these busy times.

### Plot 3
```{r warning=FALSE, echo=FALSE}
bikeshare3 <- suppressMessages(bikeshare %>%
  filter(hr == 9) %>%
    group_by(workingday, weathersit)%>%
    summarize(avg_total = mean(total, na.rm = TRUE)))
bikeshare3 <- bikeshare3 %>%
  mutate(workingday = ifelse(workingday == 1, "Working Day", "Not a Working Day"))
ggplot(bikeshare3, (aes(x=weathersit, y=avg_total)))+geom_bar(stat='identity')+facet_grid('workingday')+labs(title='Average Bike Rentals for Each Weather Situation For the 9th Hour')

```

This bar graph illustrates average bike ridership during the 9th hour of the day, taking into account different weather conditions and whether the day is a working day or not. The data reveal that in weather situation 1, both working and non-working days experience high ridership levels. A similar trend is observed in weather situation 2. However, in weather situation 3, bike ridership drops by nearly 50% for both types of days, indicating a significant impact of adverse weather. Overall, this analysis highlights that bike ridership is influenced not only by weather conditions but also by the nature of the day, whether it’s a working day or not.

# Question 3


## Part 1
```{r warning=FALSE, echo=FALSE}
capmetro<- read.csv("capmetro_UT.csv")
capmetro1 <- capmetro %>%
  group_by(hour_of_day, day_of_week, month) %>%
  summarize(avg_boarding = mean(boarding), .groups = "drop")
capmetro1$month<-factor(capmetro1$month,levels=c("Sep", "Oct", "Nov"))
capmetro1$day_of_week<-factor(capmetro1$day_of_week,levels=c("Sun","Mon","Tue","Wed","Thu", "Fri", "Sat"))

ggplot(capmetro1, aes(x = hour_of_day, y = avg_boarding, color = month, group = month)) +
  geom_line(size = 1.2) + 
  facet_wrap(day_of_week ~ .) + 
  scale_color_manual(values = c( "Sep" = "pink", "Oct" = "purple", "Nov" = "orange" )) +
  labs(
    title = "Average Boardings by Hour of Day Faceted by Day of Week",
    x = "Hour of Day",
    y = "Average Boardings",
    color = "Month") + theme_minimal() +
  theme(strip.text = element_text(size = 12, face = "bold"), legend.position = "bottom")



```

This figure displays the average boardings by day of the week for the months of September, October, and November. While peak boarding times remain generally consistent across days, there are notable fluctuations influenced by specific events. In September, average boardings on Mondays are lower, likely due to Labor Day, when schools and many workplaces are closed, resulting in decreased ridership. In November, the reduction in average boardings on Wednesdays, Thursdays, and Fridays can be attributed to the Thanksgiving holiday period. Many students and employees travel home or take time off, leading to lower boarding on these days. Although Thanksgiving affects the entire week, the impact is particularly visible on these mid-week days as people prepare for the holiday.


## Part 2
```{r warning=FALSE, echo=FALSE}
ggplot(capmetro, aes(x = temperature, y = boarding, color = weekend)) +
  geom_point(alpha = 0.4) + 
  facet_wrap(~ hour_of_day, ncol = 4) +
  labs(
    title = "Boardings vs. Temperature Faceted by Hour of the Day",
    x = "Temperature (F)",
    y = "Number of Boardings",
    color = "Day Type",
    caption = "123"
  ) +
  theme_minimal() +
  theme(
    strip.text = element_text(size = 12, face = "bold"),
    legend.position = "right"
  )

```


This figure presents the average number of people around UT riding the bus across different hours of the day, while controlling for weekend status and temperature. The data indicate that temperature does not significantly affect the number of boarding when hour of day and weekend status are held constant.This observation suggests that students and commuters maintain their transportation habits regardless of temperature fluctuations. The need to attend classes or fulfill work obligations appears to take precedence over comfort, leading to consistent ridership levels across various temperature ranges. Even in colder or hotter weather situations, they still will o to work.

# Question 4

### Part A
```{r warning=FALSE, echo=FALSE}

billboard <- read.csv("billboard.csv")

top_songs <- billboard %>%
  group_by(performer, song) %>%
  summarize(count = n(), .groups = 'drop') %>%
  arrange(desc(count)) %>%
  slice_head(n = 10)
print(top_songs)
caption <- "Table showing the top 10 most popular songs on the Billboard Top 100 since 1958 based on the total number of weeks each song spent on the chart."
cat(caption)

```


### Part B
```{r warning=FALSE, echo=FALSE}

musical_diversity <- billboard %>%
  filter(year != 1958 & year != 2021) %>% 
  group_by(year) %>%
  summarize(unique_songs = n_distinct(song), .groups = 'drop')  # Count unique songs
ggplot(musical_diversity, aes(x = year, y = unique_songs)) +
  geom_line(color = "blue") +
  labs(
    title = "Musical Diversity of the Billboard Top 100 Over Time",
    x = "Year",
    y = "Number of Unique Songs",
)+
  theme_minimal()

```


"This graph shows the number of unique songs that appeared on the Billboard Top 100 chart each year, excluding 1958 and 2021." There seems to be not a lot of diversity in early 2000's. This is likely where marketability often took precedence over artistic diversity. The success of certain pop artists and trends created a cycle where similar sounds were replicated for profit.

### Part C
```{r warning=FALSE, echo=FALSE}
ten_week_hits <- billboard%>%
  group_by(performer, song) %>%
  summarize(weeks_on_chart = n(), .groups = 'drop') %>%
  filter(weeks_on_chart >= 10)  
ten_week_hits_count <- ten_week_hits %>%
  group_by(performer) %>%
  summarize(ten_week_hits = n(), .groups = 'drop') %>%
  filter(ten_week_hits >= 30)
ggplot(ten_week_hits_count, aes(x = reorder(performer, ten_week_hits), y = ten_week_hits)) +
  geom_bar(stat = "identity", fill = "steelblue") +
  coord_flip() +  
  labs(
    title = "Artists with the Most Ten-Week Hits",
    x = "Artist",
    y = "Number of Ten-Week Hits",
    caption = "This bar plot shows the number of ten-week hits for artists who have achieved at least 30 ten-week hits on the Billboard Top 100 since 1958."
  ) +
  theme_minimal()


```

